% Autogenerated translation of WSC_18_SK.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

+++
date = 2018-10-19T00:00:00  \# Schedule page publish date.

title = "Bayesian Sequential Learning for Contextual Selection"
time\emph{start = 2018-10-19T14:30:00
time}end = 2018-10-19T16:00:00
abstract = "A typical decision making problem in practice is to select the best from a collection of alternatives. The value of each alternative, however, is unknown and can only be learned via expensive sampling. Motivated by the emerging popularity of personalized decision making in various areas including healthcare and e-commerce, we study the selection problem in the presence of contextual information, where the best alternative is not universal but depends on certain covariates. Given a limited sampling budget, we propose an adaptive sampling strategy to efficiently learn the decision rule that specifies the best alternative for a given value of the covariates. The sampling strategy is developed via a nonparametric Bayesian approach and is shown to be asymptotically optimal. We demonstrate the usefulness of our methodology via a case study in personalized medicine for selecting the best cancer treatment regimen. "
abstract\emph{short = ""
event = "Faculty of Business and Economics, University of Hong Kong"
event}url = ""
location = "Hong Kong"

\chapter*{Is this a selected talk? (true/false)}

selected = false

\chapter*{Projects (optional).}

\chapter*{Associate this talk with one or more of your projects.}

\chapter*{Simply enter the filename (excluding '.md') of your project file in \texttt{content/project/}.}

projects = ["RS"]

\chapter*{Links (optional).}

url\emph{pdf = ""
url}slides = ""
url\emph{video = ""
url}code = ""

\chapter*{Does the content use math formatting?}

math = true

\chapter*{Does the content use source code highlighting?}

highlight = true

\chapter*{Featured image}

\chapter*{Place your image in the \texttt{static/img/} folder and reference its filename below, e.g. \texttt{image = "example.jpg"}.}

[header]
image = ""
caption = ""

+++

\begin{verbatim}
<!-- Embed your slides or video here using [shortcodes](https://sourcethemes.com/academic/post/writing-markdown-latex/). Further details can easily be added using *Markdown* and $\rm \LaTeX$ math code. -->
\end{verbatim}

\end{document}
